### 2021-04-13 paper.Rmd
Section 4 information was missing
revised fig 3

\begin{figure*}[!t]
         \includegraphics[width=0.5\textwidth]{figures/cluster_example_r.pdf}
     \vfill
   \begin{minipage}{\linewidth}     
   \centering
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour1_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour2_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour3_r.pdf}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_tour4_r.pdf}
   \end{minipage}%
\caption{Comparison of structure perception between nonlinear dimension reduction using t-SNE (A) and projections seen during a tour (B.1-4). There are six clusters, as seen in the t-SNE view, but the relative distance between the clusters is extremely varied. This can be seen in the tour projections. The two green clusters are spherical in shape, and very distance from the brown clusters. Three of the brown clusters are very close to each other (just visible in B.1), and all brown clusters are elliptical. The tour provides a more accurate rendering of the clusters in the high-dimensional space, and complements what is learned from the dimension reduction.}
\label{fig:tsne-tour}
\end{figure*}

The rest of the review is structured as follows: section \@ref(notation) defines the notation and components of a tour displays. By its nature a tour is most effective to analyst when combined with interactivity; section \@ref(interaction) reviews the components of user interfaces for manipulating tour views. The implementation of tour paths in statistical software is reviewed in section \@ref(software). Section \@ref(applications) shows the diverse applications of the tour in the natural sciences, machine learning and applied statistics. Finally, section \@ref(discussion) discusses future research directions for tours.

@@

# Manual Tours

>>>>

\begin{figure*}[!t]
         \includegraphics[width=0.5\textwidth]{figures/cluster_example_r.pdf}
     \vfill
   \begin{minipage}{\linewidth}     
   \centering
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_new_tour1.png}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_new_tour2.png}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_new_tour3.png}
         \includegraphics[width=0.24\textwidth]{figures/cluster_example_new_tour4.png}
   \end{minipage}%
\caption{Comparison of structure perception between nonlinear dimension reduction from 10D, using t-SNE (A) and a tour (B). There are six clusters, as seen in the t-SNE view, but the relative distance between the clusters is extremely varied. This can be seen in sample of tour projections shown. The two green clusters are (almost) spherical in shape, and very distance from the brown clusters. Three of the brown clusters are very close to each other (just visible in B.1), and all brown clusters are elliptical. The tour provides a more accurate rendering of the clusters in the high-dimensional space, and complements what is learned from the dimension reduction.}
\label{fig:tsne-tour}
\end{figure*}

The rest of the review is structured as follows: section \@ref(notation) defines the notation and components of a tour displays. By its nature a tour is most effective to analyst when combined with interactivity; section \@ref(interaction) reviews the components of user interfaces for manipulating tour views. Section \@ref(tours) shows manual tours, these are useful to test structure of selected features. The implementation of tour paths in statistical software is reviewed in section \@ref(software). Section \@ref(applications) shows the diverse applications of the tour in the natural sciences, machine learning and applied statistics. Finally, section \@ref(discussion) discusses future research directions for tours.

@@

# Manual Tours {#tours}
